Proposed Solution

### 2016-01-29 intro1.tex
config: comments

We propose an approach to the verification of  
configuration files which is based on learning rules about the language 
model for configuration files.

>>>>

We propose an approach to the verification of  
configuration files which is based on learning rules about the language 
model for configuration files. \xxx{I think we should explicitly 
mention our approach aims to solve 
misconfiguration from different way with the
previous work. Previous work tries to find out the problem after the
failures occur, but our approach is a proactive method, which can
find out error before the system failure occurs. Such an effort (i.e., 
preventing misconfiguration before installation) is
important, because the majority of errors can be 
detected before running your system. 
Thus, 1) users will not complain too much because they are using
``very healthy'' configuration files, 
and 2) this is a great complementary to existing reactive misconfiguration 
detectors. -- Ennan}
